weather

### 2021-08-16 Manuscript/Manuscript.Rmd
hgh

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = '')
read_csv("../data/table.csv") %>% 
  janitor::row_to_names(row_number = 1) %>% 
  kable(booktabs = TRUE, caption = "Field study attributes ",
        col.names = c("Attributes",
                           "",
                           "Arlington, WI",
                           "Clay Center, NE",
                           "Grant, NE",
                      "Lincoln, NE", "Macomb, IL")) %>% 
#  pack_rows(
 #   index = c("Bareground" = 2, "Corn" = 4, "Soybean" = 8)) %>% 
  kable_styling(font_size = 12, 
                full_width = FALSE, 
                position = "center",
                latex_options = c("scale_down", "striped", "hold_position")) %>% 
  collapse_rows(columns = 1, latex_hline = "none", valign = "middle") 
```

@@

```{r table1, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/weather/Figure 1.png")
```

@@

$$Y(x) = 0 + (d-0) exp (-exp(b(log(x)-e)))$$
In this model, *Y* is the Palmer amaranth cumulative flowering, *d* is the upper limit (set to 100), and *e* is the XXX, and *x* day of year (doy).

@@

Palmer amaranth gender was fitted to a binary logistic regression [@bangdiwala2018]. Binary logistic regression is used for predicting binary classes, such gender of Palmer amaranth plants. Prior to the analysis, all missing values were removed from the dataset. Also, data from Grant was not used in this analysis due to the uniform plant harvesting at that location. The whole dataset was splitted into 80% train and 20% test data. The 80% train is used for the model training and the rest 20% is used for checking how the model generalized on unseen dataset. With 80% dataset, a binary response variable, male (0) and female (1), was fitted to a generalized linear model (*glm* function) including day of year harvest, height, weight, crop and month as independent variables. The model family was binomial with a logit function. The model fit was assessed through pseudo R squared values (McFadden, Cox and Snell, Cragg and Uhler) and likelihood ratio using *nagelkerke* function ("rcompanion" package). The marginal effects computation was performed with Average Marginal Effects at every observed value of x and average across the results (AMEs) [@leeper2017] using *margins* function from "margins" package. The rest 20% dataset was predicted using *predict* function with a cutoff estimation for male or female using *performance* function. The model quality prediction from the classification algorithm was measure with precision (*precision* function), recall (*recall* function) and F1 score (*f_meas* function) using "yardstick" package. The precision determines the accuracy of positive predictions (female plants), recall determines the fraction of positives that were correctly identified, and F1 score is a weighted harmonic mean of precision and recall with the best score of 1 and the worst score of 0. F1 score conveys the balance between the precision and the recall.

@@

The model fit was 0.11, 0.14, 0.18 with using pseudo R squared test from McFadden, Cox and Snell, and Cragg and Uhler, respectively. The likelihood ratio test showed a p-value of < 0.00. The average marginal effects showed that increasing a weight unit by 1 g increases the probability of having a female plant by 0.08% (P = 0.01). Similar trend is observed to height as well as doy, whereas the probability of being female increase by 0.2% (P = 0.01) and 0.4% (P = 0.00) when a unit of height (cm) and day increases, respectively.

The model accuracy evaluation accuracy in the unseen 20% dataset was 0.61 with a cutoff value for female and male plants of 0.49. The model classification showed a precision of 0.59, recall of 0.76, and a F1 score of 0.66. In addition, the area under the curve was 0.61.

>>>>

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = '')
read_csv("../data/table.csv") %>% 
  janitor::row_to_names(row_number = 1) %>% 
  kable(booktabs = TRUE, caption = "Field study attributes ",
        col.names = c("Attributes",
                           "",
                           "Arlington, WI",
                           "Clay Center, NE",
                           "Grant, NE",
                      "Lincoln, NE", "Macomb, IL")) %>% 
#  pack_rows(
 #   index = c("Bareground" = 2, "Corn" = 4, "Soybean" = 8)) %>% 
  kable_styling(font_size = 10, 
                full_width = FALSE, 
                position = "center",
                latex_options = c("scale_down", "hold_position")) %>% 
  collapse_rows(columns = 1, latex_hline = "none", valign = "middle") 
```

@@

```{r fig1, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/weather/Figure 1.png")
```

@@

$Y(x) = 0 + (d-0) exp (-exp(b(log(x)-e)))$

In this model, *Y* is the Palmer amaranth cumulative flowering, *d* is the upper limit (set to 100), and *e* is the XXX, and *x* day of year (doy).

@@

Palmer amaranth gender was fitted to a binary logistic regression [@bangdiwala2018]. Binary logistic regression is used for predicting binary classes, such as the probability of female in dioecious plants. Prior to the analysis, all missing values were removed from the dataset. Also, data from Grant was not used in this analysis due to the uniform plant harvesting at that location. The whole dataset was splitted into 80% train and 20% test data. The 80% train is used for the model training and the rest 20% is used for checking how the model generalized on unseen dataset. With 80% dataset, a binary response variable, male (0) and female (1), was fitted to a generalized linear model (*glm* function) including day of year harvest, height, weight, crop and month as independent variables. The model family was binomial with a logit function. The model fit was assessed through pseudo R squared values (McFadden, Cox and Snell, Cragg and Uhler) and likelihood ratio using *nagelkerke* function ("rcompanion" package). The marginal effects computation was performed with Average Marginal Effects at every observed value of x and average across the results (AMEs) [@leeper2017] using *margins* function from "margins" package. The rest 20% dataset was predicted using *predict* function with a cutoff estimation for male or female using *performance* function. The model quality prediction from the classification algorithm was measure with precision (*precision* function), recall (*recall* function) and F1 score (*f_meas* function) using "yardstick" package. The precision determines the accuracy of positive predictions (female plants), recall determines the fraction of positives that were correctly identified, and F1 score is a weighted harmonic mean of precision and recall with the best score of 1 and the worst score of 0. F1 score conveys the balance between the precision and the recall.

@@

The model fit was 0.23, 0.32, 0.40 with using pseudo R squared test from McFadden, Cox and Snell, and Cragg and Uhler, respectively. The likelihood ratio test showed a p-value of < 0.00. The average marginal effects showed that Palmer amaranth growing in corn resulted in 14.5% less females plants (Table 2). Moreover, increasing a unit doy  increases the probability of having a female plant by 0.4% (Table 2 and Figure4A). Similar trend is observed to weight as well as height, whereas the probability of being female increase by 0.2% (Figure 4B) and 0.1% (Figure 4C) when a unit of weight (g) and height (cm) increases, respectively.

```{r echo = FALSE, warning = FALSE, message=FALSE}
read_csv("../data/table_a.csv") -> table_a

#names(table_a)[2] <- paste0(names(table_a)[2], 
#                                footnote_marker_symbol(1))

table_a %>% 
  kable(booktabs = TRUE, escape = TRUE, caption = "Average marginal means of gender logistic model. Factor pararemter values (e.g. crop) is shown related to soybean.") %>% 
  kable_styling(font_size = 10, 
                full_width = FALSE, 
                position = "center",
                latex_options = c("hold_position")) %>% 
  collapse_rows(columns = 1, latex_hline = "none", valign = "middle") %>%
  footnote(
           alphabet = c("Average Marginal Effects.", "Standard Error."),
           footnote_as_chunk = TRUE)
```

The model accuracy evaluation accuracy in the unseen 20% dataset was 0.62 with a cutoff value for female and male plants of 0.43. The model classification showed a precision of 0.64, recall of 0.66, and a F means score of 0.65. In addition, the area under the curve was 0.64.

### 2021-08-16 Manuscript/Manuscript.tex
hgh

\caption{\label{tab:unnamed-chunk-2}Field study attributes }
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{lllllll}
\toprule
Attributes &  & Arlington, WI & Clay Center, NE & Grant, NE & Lincoln, NE & Macomb, IL\\
\midrule
\cellcolor{gray!6}{Bareground} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

\cellcolor{gray!6}{Corn} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

\cellcolor{gray!6}{} & \cellcolor{gray!6}{Seeding rate} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{86487} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

 & Weed control & glyphosate / S-metolachor & S-metolachlor + trazine + mesotrione, + bicyclopyrone &  &  & \\

\cellcolor{gray!6}{Soybean} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

\cellcolor{gray!6}{} & \cellcolor{gray!6}{Seeding rate} & \cellcolor{gray!6}{296400} & \cellcolor{gray!6}{321237} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

 & Weed control & glyphosate / S-metolachor & saflufenacil + imazethapyr + pyroxasulfone &  &  & \\

\cellcolor{gray!6}{Planting day} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{May 10 to 20} & \cellcolor{gray!6}{May 10 to 14} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

\cellcolor{gray!6}{} & \cellcolor{gray!6}{Type} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Crete Silt Loam} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

\cellcolor{gray!6}{} & \cellcolor{gray!6}{pH} & \cellcolor{gray!6}{6.6} & \cellcolor{gray!6}{6.5} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

 & Organic matter (\%) &  & 3 &  &  & \\
\bottomrule
\end{tabular}}
\end{table}

@@

\[Y(x) = 0 + (d-0) exp (-exp(b(log(x)-e)))\] In this model, \emph{Y} is
the Palmer amaranth cumulative flowering, \emph{d} is the upper limit
(set to 100), and \emph{e} is the XXX, and \emph{x} day of year (doy).

@@

Palmer amaranth gender was fitted to a binary logistic regression
(Bangdiwala, 2018). Binary logistic regression is used for predicting
binary classes, such gender of Palmer amaranth plants. Prior to the
analysis, all missing values were removed from the dataset. Also, data
from Grant was not used in this analysis due to the uniform plant
harvesting at that location. The whole dataset was splitted into 80\%
train and 20\% test data. The 80\% train is used for the model training
and the rest 20\% is used for checking how the model generalized on
unseen dataset. With 80\% dataset, a binary response variable, male (0)
and female (1), was fitted to a generalized linear model (\emph{glm}
function) including day of year harvest, height, weight, crop and month
as independent variables. The model family was binomial with a logit
function. The model fit was assessed through pseudo R squared values
(McFadden, Cox and Snell, Cragg and Uhler) and likelihood ratio using
\emph{nagelkerke} function (``rcompanion'' package). The marginal
effects computation was performed with Average Marginal Effects at every
observed value of x and average across the results (AMEs) (Leeper, 2017)
using \emph{margins} function from ``margins'' package. The rest 20\%
dataset was predicted using \emph{predict} function with a cutoff
estimation for male or female using \emph{performance} function. The
model quality prediction from the classification algorithm was measure
with precision (\emph{precision} function), recall (\emph{recall}
function) and F1 score (\emph{f\_meas} function) using ``yardstick''
package. The precision determines the accuracy of positive predictions
(female plants), recall determines the fraction of positives that were
correctly identified, and F1 score is a weighted harmonic mean of
precision and recall with the best score of 1 and the worst score of 0.
F1 score conveys the balance between the precision and the recall.

@@

The model fit was 0.11, 0.14, 0.18 with using pseudo R squared test from
McFadden, Cox and Snell, and Cragg and Uhler, respectively. The
likelihood ratio test showed a p-value of \textless{} 0.00. The average
marginal effects showed that increasing a weight unit by 1 g increases
the probability of having a female plant by 0.08\% (P = 0.01). Similar
trend is observed to height as well as doy, whereas the probability of
being female increase by 0.2\% (P = 0.01) and 0.4\% (P = 0.00) when a
unit of height (cm) and day increases, respectively.

The model accuracy evaluation accuracy in the unseen 20\% dataset was
0.61 with a cutoff value for female and male plants of 0.49. The model
classification showed a precision of 0.59, recall of 0.76, and a F1
score of 0.66. In addition, the area under the curve was 0.61.

@@

>>>>

\caption{\label{tab:unnamed-chunk-2}Field study attributes }
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lllllll}
\toprule
Attributes &  & Arlington, WI & Clay Center, NE & Grant, NE & Lincoln, NE & Macomb, IL\\
\midrule
Bareground &  &  &  &  &  & \\

@@

Corn &  &  &  &  &  & \\

@@

 & Seeding rate &  & 86487 &  &  & \\

\multirow{-3}{*}{\raggedright\arraybackslash } & Weed control & glyphosate / S-metolachor & S-metolachlor + trazine + mesotrione, + bicyclopyrone &  &  & \\

Soybean &  &  &  &  &  & \\

@@

 & Seeding rate & 296400 & 321237 &  &  & \\

\multirow{-3}{*}{\raggedright\arraybackslash } & Weed control & glyphosate / S-metolachor & saflufenacil + imazethapyr + pyroxasulfone &  &  & \\

Planting day &  & May 10 to 20 & May 10 to 14 &  &  & \\

@@

 & Type &  & Crete Silt Loam &  &  & \\

@@

 & pH & 6.6 & 6.5 &  &  & \\

\multirow{-4}{*}{\raggedright\arraybackslash } & Organic matter (\%) &  & 3 &  &  & \\
\bottomrule
\end{tabular}}
\end{table}

@@

\(Y(x) = 0 + (d-0) exp (-exp(b(log(x)-e)))\)

In this model, \emph{Y} is the Palmer amaranth cumulative flowering,
\emph{d} is the upper limit (set to 100), and \emph{e} is the XXX, and
\emph{x} day of year (doy).

@@

Palmer amaranth gender was fitted to a binary logistic regression
(Bangdiwala, 2018). Binary logistic regression is used for predicting
binary classes, such as the probability of female in dioecious plants.
Prior to the analysis, all missing values were removed from the dataset.
Also, data from Grant was not used in this analysis due to the uniform
plant harvesting at that location. The whole dataset was splitted into
80\% train and 20\% test data. The 80\% train is used for the model
training and the rest 20\% is used for checking how the model
generalized on unseen dataset. With 80\% dataset, a binary response
variable, male (0) and female (1), was fitted to a generalized linear
model (\emph{glm} function) including day of year harvest, height,
weight, crop and month as independent variables. The model family was
binomial with a logit function. The model fit was assessed through
pseudo R squared values (McFadden, Cox and Snell, Cragg and Uhler) and
likelihood ratio using \emph{nagelkerke} function (``rcompanion''
package). The marginal effects computation was performed with Average
Marginal Effects at every observed value of x and average across the
results (AMEs) (Leeper, 2017) using \emph{margins} function from
``margins'' package. The rest 20\% dataset was predicted using
\emph{predict} function with a cutoff estimation for male or female
using \emph{performance} function. The model quality prediction from the
classification algorithm was measure with precision (\emph{precision}
function), recall (\emph{recall} function) and F1 score (\emph{f\_meas}
function) using ``yardstick'' package. The precision determines the
accuracy of positive predictions (female plants), recall determines the
fraction of positives that were correctly identified, and F1 score is a
weighted harmonic mean of precision and recall with the best score of 1
and the worst score of 0. F1 score conveys the balance between the
precision and the recall.

@@

The model fit was 0.23, 0.32, 0.40 with using pseudo R squared test from
McFadden, Cox and Snell, and Cragg and Uhler, respectively. The
likelihood ratio test showed a p-value of \textless{} 0.00. The average
marginal effects showed that Palmer amaranth growing in corn resulted in
14.5\% less females plants (Table 2). Moreover, increasing a unit doy
increases the probability of having a female plant by 0.4\% (Table 2 and
Figure4A). Similar trend is observed to weight as well as height,
whereas the probability of being female increase by 0.2\% (Figure 4B)
and 0.1\% (Figure 4C) when a unit of weight (g) and height (cm)
increases, respectively.

\caption{\label{tab:unnamed-chunk-3}Average marginal means of gender logistic model. Factor pararemter values (e.g. crop) is shown related to soybean.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrrr}
\toprule
Term & AME & SE & Lower & Upper & Z-score & P-value\\
\midrule
crop\_bareground & -0.048 & 0.054 & -0.154 & 0.059 & -0.876 & 0.381\\

crop\_corn & -0.148 & 0.052 & -0.250 & -0.046 & -2.842 & 0.004\\

doyh & 0.004 & 0.001 & 0.003 & 0.006 & 4.959 & 0.000\\

height & 0.002 & 0.001 & 0.001 & 0.003 & 2.953 & 0.003\\

weight & 0.001 & 0.000 & 0.000 & 0.001 & 2.179 & 0.029\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textsuperscript{a} Average Marginal Effects. \textsuperscript{b} Standard Error.}\\
\end{tabular}
\end{table}

The model accuracy evaluation accuracy in the unseen 20\% dataset was
0.62 with a cutoff value for female and male plants of 0.43. The model
classification showed a precision of 0.64, recall of 0.66, and a F means
score of 0.65. In addition, the area under the curve was 0.64.

@@

{\centering \includegraphics[width=160mm,height=100mm]{../data analysis/weather/Figure 1}

\caption{Mean average temperature (C) and montly sum precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL}\label{fig:Figure-1}
\end{figure}

### 2021-08-16 data analysis/gender_analysis.Rmd
hgh

@@

```{r}
# Calculate average marginal effect
effects_logit_dia = margins(model_logi)
# Summary of marginal effect
summary(effects_logit_dia) %>% 
#For example, the AME value of height is 0.0016 which can be interpreted as a unit increase in height value increases the probability of having female by 0.16%.
tidy(effects_logit_dia) 
```
```{r}
library(reactablefmtr)
options(scipen = 999)
summary(effects_logit_dia) %>%
#  as.data.frame() %>% 
  mutate_if(is.double, ~round(., 3)) %>% 
  rename(Term = factor,
         `P-value` = p,
         Lower = lower,
         Upper = upper) %>% 
  dplyr::select(Term, AME, SE, Lower, Upper, `P-value`) %>% 
  reactable()
```

@@

```{r}
# predict the preproc_test dataset
pred <- predict(model_logi, preproc_test, type="response") 
predicted <- round(pred) # round of the value; >0.5 will convert to 
                         # 1 else 0
# Creating a contigency table
tab <- table(Predicted = predicted, Reference = preproc_test$fem)
tab
```

@@

```{r}
pred.rocr <- prediction(pred, preproc_test$fem)
eval <- performance(pred.rocr, "acc")
plot(eval)
```

>>>>

```{r}
data2 %>% 
  distinct(location)
```

@@

```{r}
# Calculate average marginal effect
effects_logit_dia = margins(model_logi)
# Summary of marginal effect
summary(effects_logit_dia) %>% 
#For example, the AME value of height is 0.0016 which can be interpreted as a unit increase in height value increases the probability of having female by 0.16%.
tidy(effects_logit_dia) 
```
```{r}
library(reactablefmtr)
options(scipen = 999)
summary(effects_logit_dia) %>%
#  as.data.frame() %>% 
  mutate_if(is.double, ~round(., 3)) %>% 
  rename(Term = factor,
         `P-value` = p,
         `Z-score` = z,
         Lower = lower,
         Upper = upper) %>% 
  dplyr::select(Term, AME, SE, Lower, Upper, `Z-score`, `P-value`) -> table_a

write_csv(table_a, "../data/table_a.csv")
```

@@

```{r}
# predict the preproc_test dataset
preproc_test <- na.omit(preproc_test)
pred <- predict(model_logi, preproc_test, type="response") 
predicted <- round(pred) # round of the value; >0.5 will convert to 
                         # 1 else 0
# Creating a contigency table
tab <- table(Predicted = predicted, Reference = preproc_test$fem)
tab
```

@@

```{r}
#preproc_test <- na.omit(preproc_test)
pred.rocr <- prediction(pred, preproc_test$fem)
eval <- performance(pred.rocr, "acc")
plot(eval)
```

### 2021-08-16 data analysis/weather/weather.Rmd
hgh

```{r}
adaptation_weather %>% 
  mutate(site = fct_recode(site, 
                           "Arlington, WI" = "Arlington",
                           "Clay Center, NE" = "Clay Center",
                           "Grant, NE" = "Grant",
                           "Lincoln, NE" = "Lincoln",
                           "Macomb, IL" = "Macomb")) -> adaptation_weather
```

@@

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  ggplot(aes(x = month_lab, y = tmean)) +
  geom_jitter(aes(color = variable), alpha = 0.05, shape = 0) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "red") +
  geom_line(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "red", shape = 22, size = 3) +
  geom_point(adaptation_weather %>% 
               filter(month %in% c(6, 7, 8, 9) & year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "blue", shape = 22, size = 3) +
  geom_richtext(data = text1, aes(x = 2, y = 7), lineheight = 0.4, 
            label = "Mean air temperature <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 6, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text2, aes(x = 2.2, y = 10), lineheight = 0.4, 
            label = "30 years <br>daily mean <br>air temperature", size = 6, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text2, 
             x = 2, y = 13, 
             xend = 2.5, yend = 16,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  scale_y_continuous(limits = c(0, 32)) +
  facet_grid(~ site) +
  labs(x = NULL, y = "Temperature (C)") +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(size = 28),
        axis.text.y = element_markdown(size = 25),
        axis.title = element_markdown(size = 27),
        axis.text.x = element_markdown(size = 25),
        legend.text = element_markdown(size = 25))  -> temp

@@

@@

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) -> adaptation_pp
```

```{r message = FALSE, warning = FALSE}
adaptation_pp %>% 
ggplot(aes(x = month_lab, y = pp)) +
  geom_bar(data = adaptation_pp %>% filter(year == c(2018, 2019)), 
           mapping = aes(fill = year),
           stat = "identity", position = "dodge", alpha = 1) +
  geom_point(data = adaptation_pp %>% filter(year != c(2018, 2019)), 
              position = position_jitter(seed = 1),
              alpha = 0.2, color = "gray50", 
              show.legend = FALSE) +
  scale_fill_manual(values = c("red", "blue")) +
  facet_grid(~ site) +
  geom_richtext(data = text3, aes(x = 2.6, y = 330), lineheight = 0.4, 
            label = "Monthly sum precipitation <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 6, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text4, aes(x = 3.6, y = 320), lineheight = 0.4, 
            label = "30 years <br>monthly sum <br>precipitation", size = 6, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text4, 
             x = 2.6, y = 310, 
             xend = 2.1, yend = 320,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  labs(x = NULL, y = "Precipitation (mm)") +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(size = 28),
        axis.text.y = element_markdown(size = 25),
        axis.title = element_markdown(size = 27),
        axis.text.x = element_markdown(size = 25),
        legend.text = element_markdown(size = 25)) -> ppp

>>>>

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  mutate(site = fct_recode(site, 
                           "Arlington, WI" = "Arlington",
                           "Clay Center, NE" = "Clay Center",
                           "Grant, NE" = "Grant",
                           "Lincoln, NE" = "Lincoln",
                           "Macomb, IL" = "Macomb")) -> adaptation_weather1
```

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site) %>% 
  summarise(tmean = mean(tmean))
```

@@

```{r}
adaptation_weather1 %>% 
  ggplot(aes(x = month_lab, y = tmean)) +
  geom_jitter(aes(color = variable), alpha = 0.05, shape = 0) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  facet_grid(~ site) +
  geom_line(adaptation_weather1 %>% 
               filter(year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "red") +
  geom_line(adaptation_weather1 %>% 
               filter(year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather1 %>% 
               filter(year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "red", shape = 22, size = 3) +
  geom_point(adaptation_weather1 %>% 
               filter(year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "blue", shape = 22, size = 3) +
  geom_richtext(data = text1, aes(x = 2, y = 7), lineheight = 0.4, 
            label = "Mean air temperature <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 6, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text2, aes(x = 2.2, y = 10), lineheight = 0.4, 
            label = "30 years <br>daily mean <br>air temperature", size = 6, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text2, 
             x = 2, y = 13, 
             xend = 2.5, yend = 16,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  scale_y_continuous(limits = c(0, 32)) +
  labs(x = NULL, y = "Temperature (C)") +
  theme_test() +
  theme(legend.position = "none",
#        strip.text = element_markdown(size = 15, hjust = 0.5),
#        axis.text.y = element_markdown(size = 25),
#        axis.title = element_markdown(size = 27),
#        axis.text.x = element_markdown(size = 25)#,
#        legend.text = element_markdown(size = 25)
        )  -> temp

@@

```{r}

@@

```{r}
adaptation_weather %>% 
  filter(month %in% c(6, 7, 8, 9)) %>% 
  group_by(month_lab, site, year) %>% 
  summarise(pp = sum(pp)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) %>% 
  mutate(site = fct_recode(site, 
                           "Arlington, WI" = "Arlington",
                           "Clay Center, NE" = "Clay Center",
                           "Grant, NE" = "Grant",
                           "Lincoln, NE" = "Lincoln",
                           "Macomb, IL" = "Macomb")) -> adaptation_pp
```

```{r message = FALSE, warning = FALSE}
adaptation_pp %>% 
ggplot(aes(x = month_lab, y = pp)) +
  geom_bar(data = adaptation_pp %>% filter(year == c(2018, 2019)), 
           mapping = aes(fill = year),
           stat = "identity", position = "dodge", alpha = 1) +
  geom_point(data = adaptation_pp %>% filter(year != c(2018, 2019)), 
              position = position_jitter(seed = 1),
              alpha = 0.2, color = "gray50", 
              show.legend = FALSE) +
  scale_fill_manual(values = c("red", "blue")) +
  facet_grid(~ site) +
  geom_richtext(data = text3, aes(x = 2.6, y = 330), lineheight = 0.4, 
            label = "Monthly sum precipitation <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 2, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text4, aes(x = 3.6, y = 320), lineheight = 0.4, 
            label = "30 years <br>monthly sum <br>precipitation", size = 2, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text4, 
             x = 2.6, y = 310, 
             xend = 2.1, yend = 320,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  labs(x = NULL, y = "Precipitation (mm)") +
  theme_test() +
  theme(legend.position = "none",
#        strip.text = element_markdown(size = 28),
#        axis.text.y = element_markdown(size = 25),
#        axis.title = element_markdown(size = 27),
#        axis.text.x = element_markdown(size = 25),
#        legend.text = element_markdown(size = 25)
  ) -> ppp
